---
title: "Fairfax County Parcel Descriptions"
author: "Allison O'Connor"
date: "October 3, 2014"
output: html_document
---

Here is some data from Fairfax County. Just a few rows of a very large file!!! This script is adapted from the one Lincoln sent me, to see if I can make changes and still have it work.
First, filter out the layout entries that do not have a value in the LENGTH field.

```{r}
layout <- read.csv("PDLayout.csv", stringsAsFactors = FALSE)
library(dplyr)
layout <- layout %>%
filter(!is.na (LENGTH))

```

Then, read the fixed width format data into a file. 

Initially, this worked with the first 100 rows, but then when I changed it to the full data file, it gave me an error at line 305, saying it did not have 142 elements. 

Eventually figured out that there were tabs and # that threw them off. Also, had to break the file into smaller pieces due to memory constraints.

```{r}
short <- read.fwf("short.txt", widths = layout$LENGTH, col.names = layout$COLUMN.NAME)
PDDataA <- read.fwf("cleanedFFXDataAA.txt", widths = layout$LENGTH, col.names = layout$COLUMN.NAME,
                    stringsAsFactors = FALSE)
PDDataB <- read.fwf("cleanedFFXDataAB.txt", widths = layout$LENGTH, col.names = layout$COLUMN.NAME,  stringsAsFactors = FALSE)
PDDataC <- read.fwf("cleanedFFXDataAC.txt", widths = layout$LENGTH, col.names = layout$COLUMN.NAME,  stringsAsFactors = FALSE)
PDDataD <- read.fwf("cleanedFFXDataAD.txt", widths = layout$LENGTH, col.names = layout$COLUMN.NAME,  stringsAsFactors = FALSE)
PDDataE <- read.fwf("cleanedFFXDataAE.txt", widths = layout$LENGTH, col.names = layout$COLUMN.NAME,  stringsAsFactors = FALSE)
PDDataF <- read.fwf("cleanedFFXDataAF.txt", widths = layout$LENGTH, col.names = layout$COLUMN.NAME,  stringsAsFactors = FALSE)
PDDataG <- read.fwf("cleanedFFXDataAG.txt", widths = layout$LENGTH, col.names = layout$COLUMN.NAME,  stringsAsFactors = FALSE)
PDDataH <- read.fwf("cleanedFFXDataAH.txt", widths = layout$LENGTH, col.names = layout$COLUMN.NAME,  stringsAsFactors = FALSE)

# take all the data pieces and bind them into one object, then remove all the little objects to free up memory.

FFXdata <- rbind(PDDataA, PDDataB, PDDataC, PDDataD, PDDataE, PDDataF, PDDataG, PDDataH)
rm(PDDataA, PDDataB, PDDataC, PDDataD, PDDataE, PDDataF, PDDataG, PDDataH)
```

Here I want to select out the columns for parcle identification, number of fireplaces, year built, land use code, and square feet of living area. This will give me the most important fields to start working with, and still preserve all the other data for future use.


```{r}
# these are the codes for various residential land uses, which I will need further down. I need this for the filter.
residential_codes <- c(011, 012, 013, 014, 015, 021, 029, 031, 032, 033, 034, 035, 036, 037, 039, 040, 041, 042, 043, 044, 045, 046, 047, 048, 049)

FFX_residential_data <- FFXdata %>%
  select(parcel_id = PARID,
        fireplace = WBFP_O...WBFP_PF,
         year_built = YRBLT,
         land_use_code = LUC,
         sqft_living_area = SFLA) %>%

  #Here I want to filter out properties with certain land use codes, so that if there are any non-residential properties in the data, I can get rid of them.
  
  filter(land_use_code%in% residential_codes) %>%
  tbl_df()

 head(FFX_residential_data)

# would there be a benefit to changing the land_use_code to a factor, since there are only certain defined values that can go in there? I could see where changing the code to a human understandable value would be helpful.

save(FFX_residential_data, "FFX_residential_data.rda")
```

Let's convert the data into a Tidy format.

```{r}
library(tidyr)
FFX_residential_data %>%
  gather(characteristic, value, -parcel_id)
```

Next I want to plot some of the data. 
Count how many homes have 0 fireplaces vs. 1 or more fireplaces and then figure out percentage.
What is the distribution of houses built over time (trying to see if there are errors in the data).
Which houses have more fireplaces? Is it related to year built, sqft of living area, something else?

```{r}
library(ggplot2)

ggplot(data = FFX_residential_data, 
       aes(x = year_built, y = fireplace))+
  geom_point()



  
 

```

```{r}
# save(my_object, "my_saved_object.rda")
# write.csv(my_object, "my_saved_object.csv")
```




